MS_CNuptake.Rmd

### 2023-05-29 MS_CNuptake.Rmd
remove rbeni functions

# Setup 
```{r setup, include=FALSE}
library(MLmetrics)
library(vhs) ##remotes::install_github("cj-holmes/vhs")
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
devtools::load_all("/Users/yunpeng/yunkepeng/latest_packages/rbeni/") # using beni's latest package.
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

#other functions
source("R/cal_nue.R")
source("R/analyse_modobs2.R")
source("R/stepwise.R")
source("R/stepwise_lm.R")
source("R/calc_area.R")

>>>>

# Setup 
```{r setup, include=FALSE}
library(MLmetrics)
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

#other functions
source("R/cal_nue.R")
source("R/plot_map3.R")
source("R/analyse_modobs2.R")
source("R/stepwise.R")
source("R/stepwise_lm.R")
source("R/calc_area.R")
source("R/nc_to_df.R")
source("R/read_nc_onefile.R")
